---
title: "Time until knee prosthesis failure with different brands in Helios Gesundheit clinics"
author: '**From:** Felipe Figueiredo **To:** Jens Freitag'
date: '**Date: ** dd/mm/aaaa'
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    reference_docx: misc/style.docx
    toc: yes
subtitle: 'REPORT: analise_dados_JF_2021-v01'
# toc-title: "Sumário"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
options(scipen = 999)
library(pander)
library(knitr)
library(philsfmisc)
panderOptions('table.style', 'rmarkdown')
panderOptions('table.split.table', Inf)
```

---

**Document version**

```{r, echo = FALSE}
Version <- c("01")
Changes <- c("Initial version")
history <- cbind(Version, Changes)
colnames(history) <- c("Version", "Alterations")
# pander(history, split.cells = 70)
kable(history)
```

---

# Abbreviations

# Introduction

## Objectives

## Data reception and cleaning

# Methods

## Variables

### Primary and secondary outcomes

### Covariates

## Statistical analyses

### Statistical packages

This analysis was performed using statistical software `R` version `r getRversion()`.
Packages used for survival analyses were `survival` version `r packageVersion("survival")` and `survminer` version `r packageVersion("survminer")`.

# Results

## Study population and follow up

## Mortality

# Exceptions and Observations

# Conclusions

# References

# Appendix

## Exploratory data analysis

## Analytical data-set

Due to confidentiality the data-set used in this analysis cannot be shared online in the public version of this report.

```{r data}
# pander(dtmin)
```
