---
title: "Statistical Analysis Plan for Association between the time to knee prosthesis failure and prosthesis brand in Helios Klinikum Berlin-Buch hospitals"
author: '**From:** Felipe Figueiredo **To:** Jens Freitag'
date: '**Date: ** dd/mm/aaaa'
output:
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    keep_md: yes
    number_sections: yes
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    reference_docx: misc/style-SAP.docx
    toc: yes
subtitle: 'SAP: SAP_analise_dados_JF_2021-v01'
# toc-title: "Sumário"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = normalizePath(".."))
options(scipen = 999)
library(pander)
library(knitr)
library(philsfmisc)
panderOptions('table.style', 'rmarkdown')
panderOptions('table.split.table', Inf)
```

---

**Document version**

```{r, echo = FALSE}
Version <- c("01")
Changes <- c("Initial version")
history <- cbind(Version, Changes)
colnames(history) <- c("Version", "Alterations")
# pander(history, split.cells = 70)
kable(history)
```

---


# Abbreviations

# Introduction

## Context

## Objectives

## Hypotheses

# Data cleaning

```{r data, include=FALSE}
source("scripts/input.R", encoding = 'UTF-8')
```

# Study variables

## Primary and secondary outcomes

## Covariates

# Statistical methods

## Statistical analyses

### Descriptive analyses

### Inferential analyses

### Statistical modeling

## Significance and Confidence Intervals

## Study size and Power

### Statistical packages

This analysis will be performed using statistical software `R` version `r getRversion()`.

# Exceptions and Observations

# References

# Appendix

